Automatic Identification and Annotation of Parallel Tasks in Structured Programs

### 2017-11-17 docs/ACM/paper.tex
Fixing one tiny typo.

To introduce Challenge~\ref{ch:cutoff}, we quote Duran {\em et al.}:
``{\em In task parallel languages, an important factor for achieving a good
performance is the use of a cut-off technique to reduce the number of tasks
created}"~\cite{Duran08}.
This observation is particularly true in the context of recursive, fine-grain,
tasks.
Figure~\ref{fig:ex_cutoff} provides such an example.
To place a limit on the number of tasks simultaneously in flight, we associate
the invocation of recursive functions annotated with task pragmas with a
counter -- \textsf{taskminer\_depth\_cutoff} in Figure~\ref{fig:cutoff}.
The guard in line 7 ensures that we never exceed \textsf{DEPTH\_CUTOFF}, a
predetermined threshold.
The code generation algorithms that we discuss in this paper are
parameterized by constants such as \textsf{DEPTH\_CUTOFF}, or
\textsf{WORK\_CUTOFF} in Figure~\ref{fig:ex_Regions}.

>>>>

To introduce Challenge~\ref{ch:cutoff}, we quote Duran {\em et al.}:
``{\em In task parallel languages, an important factor for achieving a good
performance is the use of a cut-off technique to reduce the number of tasks
created}"~\cite{Duran08}.
This observation is particularly true in the context of recursive, fine-grain,
tasks.
Figure~\ref{fig:ex_cutoff} provides such an example.
To place a limit on the number of tasks simultaneously in flight, we associate
the invocation of recursive functions annotated with task pragmas with a
counter -- \textsf{taskminer\_depth\_cutoff} in Figure~\ref{fig:ex_cutoff}.
The guard in line 7 ensures that we never exceed \textsf{DEPTH\_CUTOFF}, a
predetermined threshold.
The code generation algorithms that we discuss in this paper are
parameterized by constants such as \textsf{DEPTH\_CUTOFF}, or
\textsf{WORK\_CUTOFF} in Figure~\ref{fig:ex_Regions}.
